---
title: Blue car observation
output: html_document
---

```{=html}
<script src="https://code.jquery.com/jquery-3.7.1.min.js" integrity="sha256-/JqT3SQfawRcv/BIHPThkBvs0OEvtFFmqPF/lYI/Cxo=" crossorigin="anonymous"></script>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{js}
$(function() {
  $(".level2").css('visibility', 'hidden');
  $(".level2").first().css('visibility', 'visible');
  $(".container-fluid").height($(".container-fluid").height() + 300);
  $(window).on('scroll', function() {
    $('h2').each(function() {
      var h2Top = $(this).offset().top - $(window).scrollTop();
      var windowHeight = $(window).height();
      if (h2Top >= 0 && h2Top <= windowHeight / 2) {
        $(this).parent('div').css('visibility', 'visible');
      } else if (h2Top > windowHeight / 2) {
        $(this).parent('div').css('visibility', 'hidden');
      }
    });
  });
})
```

```{css}
library(tidyverse)

.figcaption {display: none}
body{
  background-colour: #fde0dd;
    colour: #4a004a;
    font-family: Arial, sans-serif;
}
h1, h2 {
  colour: #c51b8a;
}
```
```{r}
library(tidyverse)
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQFRCJM7Fwjtl4uehhwqLm2pf5i0mlFnStUxqGegS_VKMIa4N67lkCP0jS0NufxkLFSHOoeWLFWIgXm/pub?output=csv")
theme_colours <- c(
  "#fde0dd",
  "#fa9fb5",
  "#c51b8a",
  "#FF00FF"
)

logged_data <- logged_data %>%
  mutate(
    Timestamp = dmy_hms(Timestamp),
    day = date(Timestamp),
    hour = hour(Timestamp),
    prop_light_blue =
      light.blue / how.many.blue.cars.seen,
    time_label =
      str_to_title(time.of.day)
  ) %>%
  
  mutate(
    prop_light_blue =
    case_when(
    is.infinite(prop_light_blue) ~ NA_real_,
    TRUE ~ prop_light_blue
      )
  )
summary_data <- logged_data %>%
  group_by(time_label) %>%
  summarise(
  mean_blue =
  mean(how.many.blue.cars.seen,
  na.rm = TRUE),
  mean_light = 
  mean(light.blue,
  na.rm = TRUE),
  observations = n()
  ) %>%
  arrange(desc(mean_blue))
  Daily_data <- logged_data %>%
    group_by(day)%>% 
    summarise(
      total_blue = 
        sum(how.many.blue.cars.seen,
            na.rm = TRUE),
      total_light =
        sum(light.blue, 
            na.rm = TRUE)
    ) %>%
    arrange(day)

```
## visual data story

## Comparing light blue cars with total blue cars

```{r}
library(tidyverse)

ggplot(logged_data,
         aes(x= how.many.blue.cars.seen,
             y=light.blue,
             colour = time_label))+
    geom_point(size=3)
  labs(
    title = "relationship between total blue carsand light blue cars",
    subtitle = "1 point = 1 observation",
    x= "total blue cars seen",
    y="light blue cars seen",
    colour= "time of day",
    caption = "scatterplot of logged observations"
  )+
    scale_colour_manual(values = theme_colours)+
    theme_minimal()

```
plot2 shows that when the amount of cars seen increases so does the number of light blue cars seen. When total blue cars are between 5 and 15 the amount of light blue cars sits around 1-3.

## comparing time of day and total blue cars

```{r}
library(tidyverse)

ggplot(summary_data,
         aes(x=time_label,
             y=mean_blue,
             fill = time_label))+
    geom_col()+
    labs(
      title =  "average number of blue cars seen",
      subtitle = "comparison across times of day",
      x="time of day",
      y="average blue cars seen",
      caption="source:logged observations"
    ) +
    scale_fill_manual(values = theme_colours)+
    theme_minimal()+
    theme(legend.position = "none")

```
the average of blue cars seen seems to be the most in the afternoon and evening, mornings have the least amount of blue car seen.

## patterns throughout the day

```{r}
library(tidyverse)

ggplot(Daily_data,
         aes(x= day,
             y= total_blue))+
    geom_line(colour="#fde0dd",
              linewidth = 1.2)+
    geom_point(colour="#c51b8a",
               size=3)+
    labs(
      title = "total blue cars observed over time",
      subtitle = "daily total based on timestamps",
      x="date",
      y="total blue cars seen"
    )+
    theme_classic()
``` 
from this plot we can see my data has a huge gap which would have been when we wernt doing project 2 or 4, the most cars seen in total in one day was over 75.

